%________________________________________________________________________________________
% @author   Mohsen Mansouryar
%________________________________________________________________________________________
\documentclass[margin,line]{resume}
\begin{document}
\name{\Large Mohsen Mansouryar}
\begin{resume}


    %____________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}\vspace{2mm}
	720-72-08-01-0 Waldhaus Studentenwohnheim\hfill{+49 176 6911 4247}\\
    Waldhausweg 17, 66123 Saarbr{\"u}cken\hfill{mohsen.brian@gmail.com}\\
    Deutschland\hfill{ir.linkedin.com/in/mohsenmansouryar}
    
    %\begin{tabular}{@{} l @{\hspace{38mm}} r}
    %Department of Mathematical Sciences                 & +98 919 4653419            \\
    %Sharif University of Technology               & mansouryar@cs.sharif.edu \\
    %Azadi St., Tehran, Iran & mohsen.brian@gmail.com\\
   %Azadi St., Tehran, Iran & http://cs.sharif.edu/\sim mansouryar\\
    %\end{tabular}


    %____________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

     Image Processing \& Computer Vision, Computational Geometry, Algorithm Design \& Analysis


    %____________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

	{\bf Universit{\"a}t des Saarlandes}, Saarbr{\"u}cken, Germany\hfill {\sf Apr. 2015 - Present}\vspace{1mm}\\
	M.Sc. in {\sl Visual Computing}

    {\bf Sharif University  of Technology}, Tehran, Iran\hfill {\sf Sept. 2009 - Sept. 2014}\vspace{1mm}\\
	B.Sc. in {\sl Computer Science}\hfill {\sf GPA: 14.74/20}
    
    {\bf Shahid Soltani}, Alborz, Iran\hfill {\sf Sept. 2005 - June 2009}\vspace{1mm}\\
    {\sl National Organization for the Development of Exceptional Talents} (NODET) \vspace{1mm}\\
    High School Diploma in {\sl Mathematics and Physics}\hfill {\sf GPA: 18.9/20}

    %____________________________________________________________________________________
    % Publications
    \section{\mysidestyle Publications}

    Mohsen Mansouryar and Amin Hedayati, "Smoothing Via Iterative Averaging (SIA) A Basic Technique for Line Smoothing," International Journal of Computer and Electrical Engineering vol. 4, no. 3, pp. 307-311, 2012

	A. Hedayati, M. Mansouryar, I. Nickaein, "A New Approach to Determination of Curve Patterns for Online Character
Recognition of Cursive Scripts", ‎\textit{Archived}‎
    %____________________________________________________________________________________
    % Academic Experience
    \section{\mysidestyle Academic\\Experience}

    {\bf Teaching Assistant}\vspace{1mm}\hfill {\sf Feb. 2010 -- July 2014}\\
    {\sl Sharif University of Technology}
    \begin{list2}
        \item Advanced Programming (Java \& Python 2.X) (2nd Semester)
        \item Introduction to Computer Science (3rd Semester)
        \item Advanced Programming (Java) (8th Semester)
        \item Operating Systems (10th Semester)
    \end{list2}
    
    {\bf Presentations}\vspace{1mm}\\
     Image Representation\hfill {\sf CS Winter School at Sharif University - Mar. 2011}  \\
     Fuzzy String Searching\hfill {\sf Sharif University - May 2011}  \\
     Optical Character Recognition\hfill {\sf Sharif University - Feb. 2011}
      
     {\bf Participated Workshops}\vspace{1mm}\\
      5th International Winter School on Computational Geometry (WSCG)\\
      {\sl Amirkabir University of Technology}\hfill {\sf Feb. 2013\vspace{1mm}}\\
      Winter School on Computer Science\\
      {\sl Sharif University of Technology}\hfill {\sf Mar. 2011}
      
      {\bf Selected Projects}\vspace{1mm}\\
      Interactive Implementation of Computational Geometry Algorithms \& Geometric Objects in JAVA\\
      M. Mansouryar, S. Jahangiri\\
      Project Supervisor: Dr. Alireza Zarei\\
      {\sl Sharif University of Technology}\hfill {\sf Sept. 2013 - Dec. 2013}
      
      Steady State Detection using Statistical Parameters in an Evolutionary Optimized Self-Organizing Map\\
      M. Mansouryar, M. Heydariaan\\
      Project Supervisor: Prof. Ramin Bozorgmehri\\
      {\sl Sharif University of Technology}\hfill {\sf Jun. 2014 - Aug. 2014}
      
      An Expert System for Online SMS Spam Detection in Android\\
      M. Mansouryar, M. Heydariaan\\
      Project Supervisor: Prof. Ramin Bozorgmehri\\
      {\sl Sharif University of Technology}\hfill {\sf Jun. 2014 - Aug. 2014}

	{\bf Other}\vspace{1mm}\\
     Joined International Association of Computer Science \& IT (IACSIT)\hfill {\sf Apr. 2011}\\%
      Member NO. {\sf 80341656}
    
    \section{\mysidestyle Professional\\Experience}
    {\bf Selected Projects}
    \begin{list2}
        \vspace*{1mm}
        \item Web Developer \& SEO of Official Student Journal's Website \\
        Department of Mathematical Sciences\hfill{\sf Sharif University - Jan. 2012}
        \item Algorithm Designer, Android Developer \& Web Developer\\
        Sharif University's Official Newspaper Application (SharifDaily)\hfill{\sf Sharif University - Nov. 2013}
        \item Android UI Designer \& Co-Developer\\
        National Web Conference Network (Shooka)\hfill{\sf Behpardaz Co. Oct. 2013 - Dec. 2013}
        \item Android Developer \& Web Designer\\
        Barfak Game\hfill{\sf ProBinTech Co. Aug. 2014 - Nov. 2014}
        \item Web Developer \& Web Designer\\
        PBTGames Website\hfill{\sf ProBinTech Co. Nov. 2014 - Jan. 2015}
    \end{list2}
    Detailed list of work experience would be available upon request.
    
    {\bf Selected Open Source Contribution}
	\begin{list2}
        \vspace*{1mm}
        \item Design \& Developement  of a Modern Weblog using Django + jQuery\hfill{\sf Aug. 2011}
         \item jQuery.Riddle Text Visualization Plugin\hfill{\sf May. 2013}
        \item 2D FOW Impelemtation Using Masking for Futile Project (A 2D Unity Framework)\hfill{\sf Mar. 2013}
        \item pyRadRec، A Python Application for Automatic Recording of SHOUTcast Stations\hfill{\sf Mar. 2015}
     \end{list2}
     {\bf Other}
     \begin{list2}
        \vspace*{1mm}
        \item Developer, Web Designer\\
       {\sl ProBinTech}  \hfill{\sf Aug. 2013 - Apr. 2015}
     \end{list2}
        
    %____________________________________________________________________________________
    % Other Experience
    \section{\mysidestyle Teaching \& Other Experience}

    {\bf Teaching Programming} 
    \begin{list2}
        \vspace*{1mm}
        \item Advanced Topics in Java, Android \& Python. \hfill {\sf Feb. 2010 -- Mar. 2015}
        \item Online Python Tutorials for Beginners in Persian Language\hfill {\sf Feb. 2010 -- Apr. 2010}
    \end{list2}
     {\bf Miscellaneous} 
    \begin{list2}
        \vspace*{1mm}
		\item IT Assistant in Iran Open 2011 International Cube Competition \hfill {\sf Sep. 2011}
		\item Reached level 3 in Project Euler using Python \hfill {\sf Feb. 2010}
    \end{list2}

    %____________________________________________________________________________________
    % Selected Courses
     \section{\mysidestyle Selected Courses} 
     {\bf Sharif University of Technology}
     \begin{list2}
        \vspace*{1mm}
        \item Computer Applications In Industry (focused on Data Mining) (18.3/20) \hfill {\sf Spring 2013}
        \item Theory of Computation (17.5/20) \hfill {\sf Spring 2013}
        \item Operating Systems (20/20) \hfill {\sf Spring 2013}
        \item Principles of Computers (Computer Organization \& Design) (16/20) \hfill {\sf Spring 2012}
        \item Advanced Topics in Programming (focused on Web Dev. \& Design Patterns) (CR) \hfill {\sf Fall 2011}
        \item Analysis of Algorithms (18/20) \hfill {\sf Spring 2011}
        \item Theory of Languages \& Automata (18/20) \hfill {\sf Fall 2010}
        \item Computer Technology (focused on Android, Linux \& Software Engineering) (20/20) \hfill {\sf Fall 2010}
        \item Data Structures (19/20) \hfill {\sf Fall 2010}
        \item Discrete Mathematics (15.6/20) \hfill {\sf Spring 2010}
        \item Advanced Programming (20/20) \hfill {\sf Spring 2010}
        \item Fundamentals of Computer Programming (20/20) \hfill {\sf Fall 2009}
        \item Introduction to Management of Technology (15.8/20) \hfill {\sf Fall 2013}
        \item AI Applications in Chemical Engineering (Graduate Course) (15/20) \hfill {\sf Spring 2014}
    \end{list2}

    %____________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Computer\\Skills} 
    \textbf{Technical Knowledge}‎\\
    Android Application Development, Web Development \& Design, Game Development\vspace{1mm}\\
	‎\textbf{Programming Languages}‎\\
	 ‎‎Java, Python, Javascript, \texttt{C\#}, Erlang (Beginner), C++ (Beginner)\vspace{1mm}\\
	 ‎\textbf{Applications \& Software Packages}‎\\
	 Matlab, SAGE, Unity3D, MS Visual Studio, Adobe Lightroom\vspace{1mm}\\
	 ‎\textbf{Web Technologies}‎\\
	 ‎‎Django, ASP.Net, jQuery, AngularJS, Redis, HTML5, CSS3, Processing.js, Google App Engine (GAE)\vspace{1mm}\\
	 ‎\textbf{Other Technologies}‎\\
	 Processing, eJabberd, GeoDjango, Trac, Subversion, Git, PostgreSQL, PostGIS, MySQL, .NET, JNI\vspace{1mm}\\
	 ‎\textbf{Operating Systems}‎\\
	 Linux (Ubuntu, Fedora), Windows\vspace{1mm}\\
	 ‎\textbf{Publishing}‎\\
	\LaTeX, MS Office Pack
    
    %____________________________________________________________________________________
    % Language Skills
     \section{\mysidestyle Language Skills} 
     {\bf Farsi} Native\\
     {\bf English} Fluent\\
     {\bf Deutsch} Beginner\\
    
    
    %____________________________________________________________________________________
    % English Proficiency 
     \section{\mysidestyle English Proficiency} 
     {\bf TOEFL iBT}\vspace{1mm}\hfill {\sf Oct. 2013}\\
    Listening: 28, Speaking: 27, Reading: 26, Writing: 26\vspace{2mm}\hfill {\sf Total Score: 107/120 (\%89)}\\
    
    %____________________________________________________________________________________
    % Interests & Activities
    \section{\mysidestyle Interests \& Activities}
    {\bf Photography} \vspace{1mm}\\
    Digital Photography, Mobile Photography (Amateur)\vspace{1mm}\\
    {\bf Music} \vspace{1mm}\\
    Electronic, Ambient \& Trance Music \vspace{1mm}\\
    {\bf Sports} \vspace{1mm}\\
    Badminton, Mountain Climbing, Table Tennis, Swimming, Chess \vspace{1mm}\\
    {\bf Other} \vspace{1mm}\\
    Sci-Fi Novels, Movies, Problem Solving, Role Playing Video Games    
    
    %____________________________________________________________________________________
    % References
    \section{\mysidestyle References} 

    {\sl Available upon request.}


\begin{center}
\begin{footnotesize}
Last updated: \today \\
\end{footnotesize}
\end{center}

%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF

